%\phantomsection
%\addcontentsline{toc}{section}{Acknowledgments}
%\begin{center}
%    ACKNOWLEDGMENTS
%\end{center}
%
%\vspace{0.75in}
For most of my life, I have been a person with little to say about those that have been part of my inspiration, motivation and education. Since I am a creature of habit, please excuse my forgetfulness and thoughtlessness.\newline  \newline 
Lets start with United States Marine Corps!\\
\indent My greatest accomplishment was proving to myself that I was born a Marine. It has been an honor to know and serve amongst the likes of all my hard-working, hard-hitting, adrenaline junky Teufel Hunden. Stay thirsty my friends and Semper Fi.\\
To the Embry-Riddle Aeronautical University Prescott Campus Physics department of 2007;\\
\indent Dr.~Darrel Smith, Dr.~Nicholas A. Devereux and Dr.~Phillip Anz-Meador, I send you my everlasting gratitude for showing to me that my mind is that of a physicist, displaying overwhelming support on my education and showing patience in teaching. \\
To my colleagues at \abbr{Jlab} ;\\
\indent Dr.~Dennis Weygand, Dr.~Michael Paolone, and Dr.~Johann Goetz, the patience you have shown me is unprecedented. You have taught me the tools I needed to \emph{debug debug debug}, perform outstanding analyses and even though we agreed on nothing but science, we are still able to be great colleagues.\\
To the Old Dominion University Physics department;\\
\indent Dr. Lawrence Weinstein, thank you for showing support throughout my studies and being a rock of knowledge. \\
\indent Dr. Anatoly Radyuskin, you are always a source of well placed meaningful knowledge along a sense of humor. I thank you for all of our conversations and laughs. \\
\indent Dr. Moskov Amaryan, there are no words that I can muster to properly convey what I would like to write about the time you were my advisor. A few underrated words would be \emph{lucky}, \emph{indebted}, \emph{kindness}, \emph{patience}, and not to mention \emph{frustrating}. However, I believe the greatest thing you have taught me comes from one of your many analogies in which you stated, ``Michael, have patience, you cannot change ones rest frame.''\\
To My family; \\
Dr. Asl\i \ Tando\u{g}an my loving wife. I was smitten the first day I met you and I have been smitten with you everyday afterward. You are a great source of my happiness. I look forward to all the hard work and dedication we will input into our lives with the reward of companionship and love. Thank you for your support and honestly you have given throughout this endeavor we both have undertaken. \\
Michael-\c{C}\i nar Kunkel and future sons and daughters. When there is something you want to achieve in life, you must first understand the terrain to achievement, be willing to take necessary detours, be steadfast in your commitments, be intelligent with your falls, never be afraid to fail, and never settle for anything less than sixth gear pinned wide open. These guidelines might appear to be a lengthy list of nonsense, but throughout my life I have held onto these as if they were virtues. I have won, I have lost, I have smiled and I have pouted but I climbed my pinnacles, if only to gaze onto other crags. Whichever paths you choose, remember that ``Baba might not know, but Baba knows.''

\clearpage
