%\setcounter{chapter}{0}
%\setcounter{secnumdepth}{-1}

\chapter{Introduction and Motivation}\label{sec:intro}
The goal of this analysis is to provide insight into the mechanisms, baryon resonances and productions channels involved in \piz production for incident beam energies already explored as well as for incident beam energies in which there exists only a sparse and in some cases no amount of data.
Nucleons are composite particles, meaning they are made up of smaller constituents. To gain insight into the structure of the nucleon, physics employ baryon spectroscopy to explore for baryon resonances. Experimental, theoretical and phenomenological methods have been developed to refine and expand the known resonance masses, widths, and electromagnetic couplings~\cite{Dugger07}. Precise measurements of the cross-section and polarization asymmetries are important to extract photo-decay amplitudes and production mechanisms. Recently there has been improvement in Wide Angle Compton Scattering predictions using a General Parton Distribution (\abbr{GPD}) handbag model. This framework has also been recently adopted into \piz production~\cite{Huang2000} to describe the production as single quark excitation in photon-quark scattering.
%of   in which the production of the nucleons is considered in a 2 part soft and hard mechanism exchange.

In this analysis, we report on an experiment that was performed with the Cebaf Large Angle Spectrometer (\abbr{CLAS}) setup at the Thomas Jefferson National Accelerator Facility (\abbr{TJNAF}). The experiment used a tagged photon beam produced via bremsstrahlung from a 5.715~GeV electron beam delivered from the CEBAF accelerator. The photon beam struck a liquid hydrogen target. The reaction of interest is photoproduction of neutral pions on a hydrogen target, $\gamma p\to p\pi^0$, with subsequent Dalitz decay $\pi^0\to e^+e^-\gamma$ or standard decay plus photon conversion conversion mode $\pi^0\to \gamma\gamma\to e^+e^-\gamma$ . Neither the Dalitz decay mode of $\pi^0$ with very small branching ratio of $\sim 1.2\%$, nor the conversion mode from the main decay mode $\pi^0\to \gamma\gamma$ with branching ratio $\sim 98.8\%$ is preferred. The conversion rate of $\gamma$ to $e^+e^-$ is substantial enough that the Dalitz and the conversion process share the total statistical sample. The cross-section measurement is performed for the reaction $\gamma p\to pe^+e^-(\gamma)$ using a tagged photon beam spanning the energy interval  $E_{\gamma}=1.142$~GeV$-5.425$~GeV. In the final state of the reaction the photon is missing, $p e^+e^-$ are detected and $\pi^0$ is identified in the missing mass of the proton.

Using \epem decay products of \piz, contrary to $\gamma\gamma$ decay of \piz, along with detection of the proton allowed the experiment to run with high current. This was achieved by requiring a trigger configuration comprised of multiple charged tracks along with Cherenkov and Electromagnetic Calorimeter detection for photon beam energies $1.142$~GeV$ < E_{\gamma} < 3.6$~GeV. For photon beam energies greater than $3.6$~GeV a trigger configuration comprised of just multiple charged tracks was utilized.
\FloatBarrier
%
%
%
%
%. First we wanted to study $M_{e+e-}$ dependence of $\pi^0$ cross section, secondly and most importantly in the Dalitz decay mode final state contains three charged tracks, contrary to $\gamma\gamma$ decay, which allows to run experiment with high current, which otherwise wouldn't have been possible with single prong charged track, due to trigger and data acquisition limitations.
%\setcounter{secnumdepth}{2}
\input{intro/meson}
\input{intro/pseudoscalar_meson}
\input{intro/Theoretical_Formalism}
\input{intro/meson_decay}
%\input{intro/meson_spect}
